---
title: "Human Development and Procrastination"
author: "Jeffrey Weltman and Jordan Kassof"
date: "11/26/2017"
output:
  html_document:
    toc: true
    keep_md: true
---

# Introduction
***

Some info about high-level project info and goals

# Data Sources
***

Two primary raw data sources, discussed below.

### Procrastionation Data

Qualtrics data, very rough around the edges, various assumptions made. See codebook for
details of all columns.

### Human Development Index Data

Human Development Index maintained by UN, blah blah some info from Wikipedia. Link to source.
Explanation of which tables. Link to codebook for columns.

# Data Importing & Merging
***

The below codechunk sources the data cleaning script for our procrastination data. There is a 
commented out write.csv statement if source data is updated and you want to get local
clean copies of the new source data
```{r, message=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
source("analysis/ProcrastinationData-ImportAndTidying.R")
kable(procrastination_dims,"html",row.names=FALSE) %>%
  kable_styling(bootstrap_options = c("striped","condensed"), 
                            full_width=F, 
                            position="left")
```

The below codechunk sources the wikipedia scraping script for HDI data. There is a 
commented out write.csv statement if source data is updated and you want to get local
clean copies of the new source data
```{r, message=FALSE}
source("data/hdi-wiki-scrape.R")
```


The below codechunk merges the two datasets and saves a copy to the /data directory.
The saving step has been commented out, remove the # sign if data is updated and a new
copy of the clean and merged data is required.
```{r}
source("data/merging-hdi-and-procrastination.R")
```

# Preliminary Analysis
***

Below we source our preliminary analysis script.
```{r}
source("analysis/q4-analysis.R")
```

#### Summary Statistics

```{r}
# Print display friendly table of summary statistics for key variables
kable(summary_list, 
             col.names = c("Variable", "Min Value", "1st Quartile",
                           "Median", "Mean", "3rd Quartile", 
                           "Max Value", "Missing Count"), 
             digits = 2, 
             format = "html",
             format.args = list(scientific = FALSE)) %>%
  kable_styling(bootstrap_options = c("striped","condensed"), 
                            full_width=F, 
                            position="left")
```

### Frequency Tables

##### Gender
```{r}
kable(gender_freqs, format = "html", col.names = c("Gender", "Participants")) %>%
    kable_styling(bootstrap_options = c("striped","condensed"), 
                            full_width=F, 
                            position="left")
```

##### Work Status

```{r}
kable(workstatus_freqs, format = "html", col.names = c("Work Status", "Participants")) %>%
    kable_styling(bootstrap_options = c("striped","condensed"), 
                            full_width=F, 
                            position="left")
```

##### Occupation

```{r}
kable(occu_freqs, format = "html", col.names = c("Occupation", "Participants")) %>%
    kable_styling(bootstrap_options = c("striped","condensed"), 
                            full_width=F, 
                            position="left")
```

##### Participants by Country

```{r}
kable(pcpts_per_country, format = "html") %>%
    kable_styling(bootstrap_options = c("striped","condensed"), 
                            full_width=F, 
                            position="left")
```

##### Internal vs External Perception

```{r}
kable(matching_perception, format = "html") %>%
    kable_styling(bootstrap_options = c("striped","condensed"), 
                            full_width=F, 
                            position="left")
```

# Deep Dive
***
